Arjun Shanmugam's Senior Thesis

### 2022-12-31 writing/paper/main.tex
Updates from Overleaf

\section{Introduction} \label{sec:introduction}

\section{Literature Review} \label{sec:literature}

\section{Data} \label{sec:data}
    \subsection{Evictions Data}
    \subsection{Tax Assessment Records}
    \subsection{Zestimates}
    \subsection{Summary Statistics}
    \begin{landscape}
         \begin{table}[H]
            \centering
            \input{output/summary_statistics/tables/summary_statistics.tex}
            \caption{Caption}
            \label{tab:my_label}
        \end{table}

    \end{landscape}

\section{Results} \label{sec:result}

\section{Discussions} \label{sec:discussion}

@@

\section*{Tables} \label{sec:tab}
\addcontentsline{toc}{section}{Tables}

\section*{Figures} \label{sec:fig}
\addcontentsline{toc}{section}{Figures}

\section*{Appendix A. Placeholder} \label{sec:appendixa}
\addcontentsline{toc}{section}{Appendix A}

>>>>

\section{Introduction} \label{sec:introduction}
\subsection{Literature Review}

\section{Institutional Context}
    \subsection{Eviction in Massachusetts}
        \subsubsection{The Massachusetts Housing Court}
        \subsubsection{The Eviction Process}
    \subsubsection{Property Tax Assessment}
        \subsubsection{The Property Value Assessment Process}
    \subsection{Zestimates}
        \subsubsection{How Are Zestimates Produced?}
        \subsubsection{Reliability}
\section{Data} \label{sec:data}
    \begin{landscape}
    \subsection{Evictions Data}
        \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/evictions_map.png}
            \caption{Spatial Incidence of Eviction}
            \label{fig:my_label}
        \end{figure}
    \end{landscape}
    \subsection{Tax Assessment Records}
    \subsection{Zestimates}
        \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/trends_in_zestimates.png}
            \caption{Trends in Zestimates}
            \label{fig:my_label}
        \end{figure}
    \begin{landscape}
    \subsection{Summary Statistics}
         \begin{table}[H]
            \centering
            \tiny
            \input{output/summary_statistics/tables/summary_statistics.tex}
            \caption{Summary Statistics}
            \label{tab:table_1}
        \end{table}
        \newpage
        \begin{table}[H]
            \centering
            \tiny
            \input{output/summary_statistics/tables/balance_table.tex}
            \caption{Balance Table}
            \label{tab:my_label}
        \end{table}
    \end{landscape}

\section{Empirical Strategy: Difference-in-Difference}
    \subsection{Estimating the ATT in the Staggered Treatment Case}
    I will use Callaway and Sant'Anna' (2021)'s multiperiod, staggered treatment difference-in-difference estimators. The following bullets summarize the empirical strategy informally; this information will eventually be placed appropriately into the subsection headers below this brief summary.
    \begin{enumerate}
        \item Reject conventional TWFE-DiD estimator. This estimator essentially estimates the ATT by performing a bunch of 2 unit, 2 period DiDs, then averages the calculated treatment effects. Goodman-Bacon (2021) shows that this estimator is composed in part of DiD estimates involving \emph{two units which are both treated during both periods}. This is in violation of the spirit of DiD. These incorrect DiD estimates are known as ``forbidden comparisons.''
        \item The way to properly recover the ATT is to basically perform all of the ``non-forbidden'' comparisons possible in our panel dataset. More formally:
        \begin{enumerate}
            \item We begin with a panel dataset of properties whose Zestimates are observed monthly. At each property $i$, an eviction case concludes during month $G_i=g$, resulting in a plaintiff victory or a defendant victory. These properties are collectively known as ``cohort $g$.'' If the eviction case at property $i$ resulted in a defendant victory, let $C_i=1$
            \item Break the units into ``cohorts'' according to the month in which their cases conclude. 
            \item We estimate $ATT(g, t)$, which is the average treatment effect on the treated for cohort $g$ at time $t$, by calculating the sample analog of:

            $E[Y_t - Y_{g-1}|G=g] - [Y_t - Y_{g-1}|C=1]$

            \item Intuitively, $ATT(g, t)$ comes from 2 period, 2 unit difference in difference estimate. The treatment group contains all units where we observe a plaintiff victory and the case was resolved at time $g$. The control group contains all units where we observe a defendant victory and the case was resolved at time $g$. We adjust the change in observed outcomes in the treatment group by the change in observed outcomes in the control group to get our estimate.

        \end{enumerate}
        \item The parallel trends and no anticipation assumptions are extended to the staggered treatment context.
            \begin{enumerate}
                \item \textbf{Staggered Treatment Adoption Assumption.} Let $D_it=1$ if unit $i$ has been treated by period $t$ and $D_it=0$ otherwise. Then, for $t=1,...,\tau$, $D_{it}=1 \rightarrow D_{it+1} = 1$. Basically, once a unit becomes treated, it stays treated.

                \item \textbf{Parallel Trends Assumption Based On Never Treated Units}. For all $g=2,...,\tau, t=2,...,\tau$ with $t\geq g$, we have

                $E[Y_t(0)-Y_{g-1}(0)|G=g]$ = $E[Y_t(0)-Y_{g-1}(0)|C=1]$

                Basically, for every possible 2 unit, 2 period DiD that we can run in our panel dataset between treated units and never-treated units, the canonical parallel trends assumption holds.

                \item \textbf{Parallel Trends Assumption Based On Not Yet Treated Units}. For all $g=2,...,\tau, s, t=2,...,\tau$ with $t \geq g$ and $s \geq t$, we have

                $E[Y_t(0) - Y_{t-1}(0)|G=g] = E[Y_t(0) - Y_{t-1}(0)|D_s=1, G \neq g]$

                This assumption allows us to use \emph{not yet treated} observations as a comparison group for \emph{treated} units. This is clearly a stronger assumption than the previous one and I have to think hard about whether I can make it in my case. Note that the graph in section 5.3 does NOT make this assumption.

            \end{enumerate}
        \item Now, we have a bunch of $ATT(g, t)$s. How do we aggregate them?
            \begin{enumerate}
                \item Take frequency-weighted averages across $t$ to get $ATT(g)$s, or ATTs for each cohort.
                \item Take frequency-weighted averages across $g$ to get $ATT(t)$s, or ATTs for each time period.
                \item Most convincing: calculate event time $e = t - g$. Now, $ATT(g, e_i)$ expresses the ATT on cohort $g$ at time relative to the end of the eviction case involving property $i$. Take frequency weighted averages across $g$ to get $ATT(e)s$, or ATTs for each period relative to the treatment period.
            \end{enumerate}
    \end{enumerate}
    \subsection{Parallel Trends Assumptions in the Staggered Treatment Case}

        \subsection{Testing Parallel Trends Empirically Using Rambachan and Roth (2022)}
    \subsection{Aggregating Treatment Effects Across Cohort and Time}
        \subsubsection{ATTs Across Cohorts}
        \subsubsection{ATTs Across Time Periods}
        \subsubsection{Event-Study ATTs}

\section{Results} \label{sec:result}
    \subsection{ATTs Across Cohorts}
    \subsection{ATTs Across Time Periods}
    \subsection{Event-Study ATTs}
        \begin{figure}[H]
            \centering
            \includegraphics{output/DiD/figures/att_gt_estimates_event_study.png}
            \caption{$ATT(e)$s}
            \label{fig:my_label}
        \end{figure}

@@

% \section*{Tables} \label{sec:tab}
% \addcontentsline{toc}{section}{Tables}

% \clearpage

% \section*{Figures} \label{sec:fig}
% \addcontentsline{toc}{section}{Figures}

% \clearpage

% \section*{Appendix A. Placeholder} \label{sec:appendixa}
% \addcontentsline{toc}{section}{Appendix A}
